RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-08 manuscripts/manuscript.Rmd
load birds nexml first

```{r echo=FALSE}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

@@

```{r eval=FALSE fig.show="hide"}
tb_nex <- nexml_read(
"https://raw.github.com/TreeBASE/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
plot(tb_phy[[1]]) 
```

@@

```{r}
prefixes <- get_namespaces(birds)
prefixes["dc"]
```

>>>>

```{r echo=FALSE, eval=FALSE}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

@@

```{r eval=FALSE, fig.show="hide"}
tb_nex <- nexml_read(
"https://raw.github.com/TreeBASE/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
plot(tb_phy[[1]]) 
```

@@

```{r}
birds <- nexml_read("birds.xml")
prefixes <- get_namespaces(birds)
prefixes["dc"]
```
